\section*{Laboratory work \#2}
\phantomsection

\section{Purpose of the laboratory}
Gain knowledge about child windows and basics of working with keyboard.
\section{Laboratory Work Requirements}
\begin{itemize}
\item \textbf{Basic Level (grade 5 - 6) you should be able to:}
	\begin{enumerate}
	\item Create a Windows application what will dispaly a dialog box on some event (ex. on clicking some button)
    \item Add a system menu to your application with at least 3 items (add actions to that items)
    \item Hook keyboard input. Add 2 custom events for 2 different keyboard combinations (ex. change window background on ctrl+space) 
	\end{enumerate}
	
\item \textbf{Normal Level (grade 7 - 8) you should be able to:}
      \begin{enumerate}
    \item Realize the tasks from Basic Level.
    \item Add a scroll bar that will change any visible parameter of any other element (color of a text) OR other 2 scroll bars that will manage main window size or position
          \end{enumerate}
          
\item \textbf{Advanced Level (grade 9 - 10) you should be able to:}
      \begin{enumerate}
    \item Realize the tasks from Normal Level.
    \item Customize your application by adding an icon and using different cursor in application
    \item Add a listbox and attach some events when any element is accessed (clicked)
          \end{enumerate}
          
\item \textbf{Bonus point task:}
      \begin{enumerate}
    \item Use a scroll bar to scroll through application working space. Scroll should appear only when necessary (eg. when window width is smaller than 300px)
    	\end{enumerate}
    	
  \end{itemize}  

\clearpage